Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2017-03-24 paper/presentation/DASFAA_presentation.tex
finish the first page

The conditional probability \(p(w|d)\) is the combination of \textbf{word-topic distribution} \(p(w|t_i)\) and \textbf{topic-document distribution} \(p(t_i|d)\).
\begin{equation}
\label{eq:tm}
	p(w|d)=\sum_{i=1}^{K} p(w|t_i)p(t_i|d)
\end{equation}

Equation (\ref{eq:tm}) equals to the following form:
\begin{equation}
\label{eq:nnv_tm}
p(w|d)=\phi(w) \theta^T(d)
\end{equation}
, where \(\phi(w)\) is the row vector \textbf{word-topic distribution} \([p(w|t_1), \cdots, p(w|t_K)]\), and \(\theta(d)\) is the row vector \textbf{topic-document distribution} \([p(t_1|d), \cdots, p(t_K|d)]\).

@@

In equation (\ref{eq:nnv_tm}), the distributions \(\phi(w)\) and \(\theta(d)\) have the following explanation:
\begin{enumerate}
	\item \(\phi(w)\) functions as the look-up layer for words with the \textbf{sigmoid} activation functions.
	\item \(\theta(d)\) functions as the look-up layer for documents with the \textbf{softmax} activation function. 
\end{enumerate}

>>>>

Many Web applications need the \textbf{accurate event detection} technique on microblog stream, including:
\begin{enumerate}
	\item public opinion analysis [Chen, SIGIR 2013]
	\item public security [Li, ICDE 2012], [Imran, WWW 2014]
	\item disaster response [Sakaki,WWW2010]
	\item breaking news report\footnote{\url{http://www.theverge.com/2016/12/1/13804542/reuters-algorithm-breaking-news-twitter}}
\end{enumerate}	
\vfill

But detecting events on twitter stream accurately is still challenging.
\end{frame}

@@
